---
title: "Test Data Distribution"
author: "Nathan Pratt - Pond"
date: "11/9/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)

library(ggplot2)
library(dplyr)
library(knitr)
```

## Distribution

The intent is to create a steep decay function where most entities have a value of 1, but rarely very high values can be obtained.

$$
\lambda e^{-\lambda (1-z)} \quad \textrm{where} \quad
z = \lambda _2 e^{-\lambda _2 x} \quad |\quad x \in [0,\infty)
$$

If we were to plot this function, it would look like the following

```{r, fig.show='hide'}
scale1 = 1
scale2 = 0.6
lambda_1 = 1/scale1
lambda_2 = 1/scale2
tmp = curve(lambda_1 * exp(-lambda_1 * (1 - (lambda_2 * exp(-lambda_2 * x)))), from = 0, to = 50)
```
```{r, out.width=c("50%", "50%"), fig.show='hold'}
ggplot(data.frame(tmp)) + 
  geom_line(aes(x, y))

z = rexp(500, scale2)
vals = ceiling(lambda_1 * exp(-lambda_1 * (1 - z)))
ggplot(data.frame(vals = vals)) + 
  geom_histogram(aes(vals))
```

```{r, results='asis'}
cat("\\twocolumn")
```

## General formatting

Formatting can be done via a couple methods. **Rmarkdown** has several built in shortcuts for manipulating your *\textcolor{red}{text}*. In an html document you can also wrap the text in elements and set the color with <span style="color: red;">CSS</span>

[Links](https://1904labs.com/) can also be included with display text or raw <https://1904labs.com/>

\break

```{r, fig.cap="plot in a column"}
ggplot(data.frame(vals = vals)) + 
  geom_histogram(aes(vals))
```


```{r, results='asis'}
cat("\\onecolumn")
```

## Tables

***

### Below we will observe several values from the same table.

```{r}
df = data.frame(as.list(summary(vals)))
```

*Print out table*

```{r}
df
```

*Default Kable*

```{r}
df %>% kable(row.names = F)
```

*Latex*

```{r}
df %>% kable(row.names = F, format = "latex")
```

*Html*

```{r}
df %>% kable(row.names = F, format = "html")
```

*Pipe*

```{r}
df %>% kable(row.names = F, format = "pipe")
```

*Simple*

```{r}
df %>% kable(row.names = F, format = "simple")
```

*RST*

```{r}
df %>% kable(row.names = F, format = "rst")
```


*Example where the table runs over a page*

```{r}
data.frame(val = vals) %>% 
  group_by(val) %>%
  count() %>% data.frame() %>%
  kable(row.names = F)
```

